\documentclass[10pt,letterpaper]{article}

\usepackage[margin=0.75in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=1.2em, topsep=0.2em, itemsep=0.25em}
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]

\begin{document}

{\LARGE \textbf{Aastha Ojha}}\\[0.25em]
Bengaluru \textbar{}
\href{mailto:asthaojha0105@gmail.com}{asthaojha0105@gmail.com} \textbar{}
\href{tel:+919900674035}{+91 99006 74035} \textbar{}
\href{https://www.linkedin.com/in/aastha-ojha/}{linkedin.com/in/aastha-ojha} \textbar{}
\href{https://github.com/aasthasd2}{github.com/aasthasd2} \textbar{}
\href{https://medium.com/@aasthaojhaa}{medium.com/@aasthaojhaa}

\vspace{0.6em}

\section*{Professional Summary}
Lead Software Engineer with 8+ years of experience architecting and delivering AI-driven, cloud-native applications. Specialized in Generative AI (GenAI) and Agentic AI, with hands-on expertise in prompt engineering and AI evaluation. Proven track record leading cross-functional teams, embedding AI agents across the SDLC, and shipping scalable systems on AWS that measurably improve velocity, reliability, and customer experience.

\section*{Professional Experience}
\textbf{EPAM Systems} \hfill \textit{May 2022 -- Present}\\
\textit{Lead Software Engineer}
\begin{itemize}
\item Led an agile cross-functional team of 8+ engineers, leveraging AI-powered tools (GitHub Copilot, Claude, ChatGPT) for code generation, reviews, and documentation, cutting deployment time by 20\% via enhanced CI/CD with GitLab and Jenkins.
\item Designed and integrated autonomous AI agents for automated code analysis, bug detection, and test case generation, improving code quality and reducing manual review effort.
\item Integrated Datadog, BigPanda, and AI-based monitoring for proactive alerting and root cause analysis, reducing debugging time by 50\%.
\end{itemize}

\textbf{Persistent Systems} \hfill \textit{Nov 2020 -- May 2022}\\
\textit{Lead Software Engineer}
\begin{itemize}
\item Architected and integrated distributed data pipelines handling large-scale data from multiple warehouses using AWS S3, DynamoDB, and Snowflake.
\item Implemented real-time and batch data processing with Avro event files and Kafka.
\item Developed a data visualization UI from scratch.
\item Automated data parity checks and checkpointing.
\end{itemize}

\textbf{Manhattan Associates} \hfill \textit{Jul 2019 -- May 2020}\\
\textit{Software Engineer}
\begin{itemize}
\item Enhanced allocation, replenishment, and inventory features in WMOS (Warehouse Management Operating System).
\item Fixed critical defects in client environments.
\end{itemize}

\textbf{Nagravision, Kudelski Security} \hfill \textit{Jun 2018 -- Jun 2019}\\
\textit{Software Engineer}
\begin{itemize}
\item Developed REST APIs and internal UI for IoT security lifecycle management.
\item Utilized ReactJS, HTML, CSS, Bootstrap, SOAP UI, and JUnit.
\end{itemize}

\textbf{Kerv Digital} \hfill \textit{Sep 2017 -- Jun 2018}\\
\textit{Software Engineer}
\begin{itemize}
\item Implemented customer-driven feature enhancements for Microsoft CRM and resolved high-priority bugs.
\item Supported issue triage and prioritization to keep delivery on track.
\end{itemize}

\section*{Technologies}
\textbf{Programming Languages:} Java, Spring, Python, JavaScript, Node.js, SQL, MySQL\\
\textbf{Generative AI \& LLMs:} GenAI, Agentic AI, Prompt Engineering, Fine-tuning, Embeddings, Semantic Search, MCP, Multimodal AI\\
\textbf{AI/ML Tools \& Platforms:} GitHub Copilot, Claude, ChatGPT, OpenAI API\\
\textbf{DevOps, Cloud \& LLMOps:} AWS, Docker, Kubernetes, Terraform, Jenkins, GitLab, Bitbucket, CI/CD, MLOps, LLMOps\\
\textbf{Data \& Analytics:} Snowflake, Oracle, Hive, Datadog, BigPanda\\
\textbf{Testing:} JUnit, Mockito, AI-powered unit test generation, TDD\\
\textbf{Other Technologies:} Redis, RabbitMQ, Kafka, Postman, SOAP UI, REST APIs, React, HTML, CSS, Bootstrap, Jira, Confluence\\
\textbf{Methodologies:} Agile, Scrum, Kanban, DevSecOps, Continuous Delivery, AI-driven development, Responsible AI / AI Governance

\section*{Education}
\textbf{College of Engineering Roorkee} \hfill \textit{Aug 2013 -- Apr 2017}\\
\textit{Bachelor of Technology in Computer Science}\\
GPA: 8.20

\end{document}
